\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}


% Style section headings
\titleformat{\section}{\large\mdseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Custom list styling for resume bullet points
\setlist[itemize]{leftmargin=0.15in, rightmargin=0in, topsep=2pt, itemsep=1pt, parseitemsep=0pt}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	HEADING
%----------------------------------------------------------------------------------------
\noindent
{\LARGE\bfseries Hitesh Ahirwar} \\[5pt]
\textit {Delhi, India \textbar{} +91 9667098949 \textbar{} hitesh.ahi.w@gmail.com \textbar{} \href{https://github.com/hiteahi}{@github} \textbar{} \href{https://www.linkedin.com/in/hiteahi}{@linkedin}}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section{PROFESSIONAL SUMMARY}
 Data Analyst and Power BI Developer skilled in Excel, SQL, Python, and automated data extraction. Experienced in building end-to-end analytics pipelines, translating raw unstructured data into clean datasets, and designing high-impact, interactive dashboards to drive business decisions.

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\noindent
\textbf{Microsoft Excel} \textbar{} Skill Course \hfill Nov 2025 \\
\textbf{Microsoft Power BI} \textbar{} Skill Course \hfill Nov 2025 \\
\textbf{SQL Course} \textbar{} Skill Course \hfill Nov 2025

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\noindent
\textbf{Languages:} Python, MySQL\\
\textbf{Tools:} Power BI, Advanced Excel, Git, Jupyter Notebook, VS Code, Power Query \\
\textbf{Libraries:} Pandas, NumPy, Matplotlib, Seaborn, Plotly, ScraperAPI \\
\textbf{Core Competencies:} Data Cleaning, Web Scraping, DAX Measures, ETL Pipelines, Intelligence Dashboarding 

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}
\noindent
\textbf{E-Commerce Operations} \textbar{} SM Store 18 \hfill Nov 2025 – May 2026 
\begin{itemize}
    \item Managed day-to-day order processing and data flows across major marketplace platforms including Amazon, Flipkart, and Meesho.
    \item Maintained and updated extensive product catalogs, ensuring consistent integrity across pricing matrices, stock levels, and technical inventory records.
    \item Engineered structured Excel reporting templates to monitor stock levels, successfully mitigating overstocking risks and preventing platform stockouts.
    \item Transformed raw operational logs into structured formats, laying the groundwork for downstream sales trend analyses and inventory performance insights.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\noindent
Govt. Bapu College, Nowgong \hfill \textbf{} {\bfseries Bachelor of Arts} \hfill  \,|\, \textit{2024 - Ongoing}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\textbf{Starbucks Daily Sales Dashboard} \textbar{} {Multi Pages Report, Dynamic Filtering, Bookmarks} \textbar{} \hfill May 2026 - June 2026
\begin{itemize}
    \item  The Starbucks Daily Sales Dashboard is an interactive Power BI project designed to analyze daily sales performance across Starbucks stores. The dashboard provides insights into orders, customers, revenue, and quantity sold while allowing users to switch between multiple visual themes.
\end{itemize}
\newline
\textbf{Uber Performance Insights Dashboard} \textbar{} {Multi Pages Report, } \textbar{} \hfill Apr 2026 - May 2026
\begin{itemize}
    \item  The Uber Performance Insights Dashboard is an interactive Power BI project designed to analyze ride bookings, revenue performance, customer behavior, vehicle utilization, and location-based trends.
    \item The dashboard provides business stakeholders with a comprehensive view of operational performance through multiple analytical pages, dynamic filtering, bookmarks, and KPI tracking.
\end{itemize}
\newline
\noindent
\textbf{E-Commerce} \textbar{} {Data Cleaning, Visualizations, Dashboard} \textbar{} \hfill Mar 2026 - May 2026
\begin{itemize}
    \item  Built an end-to-end e-commerce analytics solution by cleaning raw transactional data, modeling datasets, and creating an interactive Power BI dashboard with revenue tracking, customer insights, return analysis, and business KPIs.
\end{itemize}
\newline
\textbf{Weather Analytics Dashboard} \textbar{} {WeatherAPI, Power Query, Advanced DAX Measures} \textbar{} \hfill Mar 2026 - Apr 2026
\begin{itemize}
    \item  Built an interactive real-time weather analytics dashboard in Power BI using WeatherAPI integration, Power Query JSON transformation, and advanced DAX measures to visualize forecasts, AQI metrics, and multi-city climate insights.
\end{itemize}


    
\end{document}